---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# myTridge

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/mohan-zhao/myTridge.svg?branch=master)](https://travis-ci.com/mohan-zhao/myTridge)
<!-- badges: end -->

The goal of myTridge is to show that ridge esti-
mators can be modified such that tuning parameters can be avoided altogether and apply the t-ridge estimator to generalized linear models.

## Installation

You can install the released version of myTridge from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("myTridge")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mohan-zhao/myTridge")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(myTridge)
## Here "gaussian" is from three most common cases for the distribution F: Gaussian,Poisson, and Bernoulli.
### high dimensional X :100x300
### k is the magnitude of the mutual correlations for covariance matrix 
TridgeEst(Test.case="gaussian",num.obs = 100,num.par=300,k=0.0)
```

```{r cars}
## example of relativeError() function
###shows t-ridge outperforms K-fold cross-validated ridge
relativeError("gaussian",100,300,0.0,5)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.
