---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# myTridge

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/mohan-zhao/myTridge.svg?branch=master)](https://travis-ci.com/mohan-zhao/myTridge)
<!-- badges: end -->

The goal of myTridge is to show that ridge esti-
mators can be modified such that tuning parameters can be avoided altogether and apply the t-ridge estimator to generalized linear models.

## Installation

You can install the released version of myTridge from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("myTridge")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mohan-zhao/myTridge")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r,warning=FALSE}
library(myTridge)
devtools::load_all()
## Here "gaussian" is from three most common cases for the distribution F: Gaussian,Poisson, and Binomial.
### X and y are matrix and vector under gaussian distribution in data folder
### dimension of X :100x300
### generate a tridge estimator
TridgeEst(Test.case="gaussian",X=X_gau,y=y_gau)
```

```{r example}

### You can also use genDataList() function in this package to generate a high dimensional matrix X and y randomly then generate a tridge estimator
list<-genDataList(n=100,mu=rep(0,300),p=300, rho=0.,beta=rnorm(300, mean = 0, sd = 1),SNR=10,Test_case="binomial")
X<-list$normData
y<-list$y
myTridge::TridgeEst(Test.case="binomial",X=X,y=y)

```


```{r,echo=FALSE}
## example of relativeError() function
###shows t-ridge outperforms K-fold cross-validated ridge by generate X and y for num.runs times randomly
### dimension of X: num.obs x num.par
### k is magnitude of the mutual correlations when generating X
myTridge::relativeError(Test.case="gaussian",num.obs=100,num.par=300,k=0.,num.runs=5)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.
